\chapter{References}
\label{chap:references}

\begin{thebibliography}{9}

\bibitem{aiscore}
“AiScore - Live Score, Football Score Today.” Accessed January 19, 2025. \url{https://www.aiscore.com/}.

\bibitem{bundesliga}
“Bundesliga | Official Website.” Accessed January 19, 2025. \url{https://www.bundesliga.com/en/bundesliga}.

\bibitem{fcbayern}
“FC Bayern Munich - Official Website | FCB.” Accessed January 19, 2025. \url{https://fcbayern.com/en}.

\bibitem{footballitalia}
“Football Italia | Italian Football News, Analysis, Fixtures and Results for the Latest from Serie A, Serie B and the Azzurri. - Football Italia.” Accessed January 19, 2025. \url{https://football-italia.net/}.

\bibitem{101greatgoals1}
“Football Live Streaming, Betting Tips, News \& Videos | 101 Great Goals.” Accessed January 18, 2025. \url{https://www.101greatgoals.com/}.

\bibitem{101greatgoals2}
“Football Live Streaming, Betting Tips, News \& Videos | 101 Great Goals.” Accessed January 19, 2025. \url{https://www.101greatgoals.com/}.

\bibitem{footballmanager}
“Football Manager Video Games - Official Site.” Accessed January 19, 2025. \url{https://www.footballmanager.com/}.

\bibitem{fourfourtwo}
“Football News, Features and Statistics | FourFourTwo.” Accessed January 19, 2025. \url{https://www.fourfourtwo.com/}.

\bibitem{whoscored1}
“Football Statistics | Football Live Scores | WhoScored.Com.” Accessed January 19, 2025. \url{https://www.whoscored.com/}.

\bibitem{whoscored2}
“Football Statistics | Football Live Scores | WhoScored.Com.” Accessed January 19, 2025. \url{https://www.whoscored.com/}.

\bibitem{transfermarkt}
“Football Transfers, Rumours, Market Values and News | Transfermarkt.” Accessed January 19, 2025. \url{https://www.transfermarkt.com/}.

\bibitem{football365}
“Football365 - Football News, Transfers, Tables, Stats, Fixtures and Results.” Accessed January 19, 2025. \url{https://www.football365.com/}.

\bibitem{onefootball}
“Home | OneFootball.” Accessed January 19, 2025. \url{https://onefootball.com/en/home}.

\bibitem{laliga}
“LALIGA Official Website | LALIGA.” Accessed January 19, 2025. \url{https://www.laliga.com/en-EG}.

\bibitem{livescore}
“Live Football Scores, Fixtures \& Results | LiveScore.” Accessed January 19, 2025. \url{https://www.livescore.com/en/}.

\bibitem{fcbarcelona}
“Official FC Barcelona Website.” Accessed January 19, 2025. \url{https://www.fcbarcelona.com/en}.

\bibitem{manutd}
“Official Manchester United Website.” Accessed January 19, 2025. \url{https://www.manutd.com/}.

\bibitem{premierleague}
“Premier League Live Scores, Stats \& Blog | 2024/25.” Accessed January 19, 2025. \url{https://www.premierleague.com/matchweek/18411/blog}.

\bibitem{theathletic}
“Soccer News - Results, Fixtures, Scores, Stats, and Rumors - The Athletic.” Accessed January 19, 2025. \url{https://www.nytimes.com/athletic/football/}.

\bibitem{squawka}
“Squawka | Football News, Stats, Quizzes \& Predictions | EPL.” Accessed January 19, 2025. \url{https://www.squawka.com/en/}.

\bibitem{anfieldwrap}
“The Anfield Wrap - Liverpool FC Podcast, Videos \& Writing.” Accessed January 19, 2025. \url{https://www.theanfieldwrap.com/}.

\bibitem{uefa}
“The Official Website for European Football | UEFA.Com.” Accessed January 19, 2025. \url{https://www.uefa.com/}.

\bibitem{jerseywatch}
“Top-Rated Sports Team Management Platform - Jersey Watch | Jersey Watch.” Accessed January 19, 2025. \url{https://www.jerseywatch.com/}.

\bibitem{worldsoccertalk}
“World Soccer Talk - TV Schedules and Streaming Links, News and Podcasts.” Accessed January 19, 2025. \url{https://worldsoccertalk.com/}.

\bibitem{goal}
“أخبار كرة القدم، بث مباشر ومواعيد ونتائج المباريات، صفقات وانتقالات | مصر Goal.Com.” Accessed January 18, 2025. \url{https://www.goal.com/ar-eg}.

\bibitem{soccerway}
“نتائج حية، نتائج، مباريات، جداول، إحصاءات وأخبار - Soccerway.” Accessed January 19, 2025. \url{https://ar.soccerway.com/}.

\bibitem{copa90}
Accessed January 19, 2025. \url{https://www.copa90.com/}.

\end{thebibliography}